---
title: "STOR556 Project"
date: "4/17/2018"
output:
  html_document: default
  pdf_document: default
header-includes: \usepackage{amsgen,amsmath,amstext,amsbsy,amsopn,amssymb,mathabx,amsthm,bm,bbm}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
if(!require(MASS)) { install.packages("MASS", repos = "http://cran.us.r-project.org"); library(MASS) }
if(!require(dplyr)) { install.packages("dplyr", repos = "http://cran.us.r-project.org"); library(dplyr) }
if(!require(ISLR)) { install.packages("ISLR", repos = "http://cran.us.r-project.org"); library(ISLR) }
if(!require(car)) { install.packages("car", repos = "http://cran.us.r-project.org"); library(car) }
```

```{r}
#Import Tidy data
crimes = read.csv("crimes_tidy.csv")
```

```{r}
#Add variable 'night' for crimes that occur between 8pm - 6am
crimes = mutate(crimes, night = 0)
crimes$night <- ifelse( crimes$hour_occur >= 20 | crimes$hour_occur <= 5, 1, 0)  
```


```{r}
#Randomly divide the data into a training and test set with ratio 3:1
n <- nrow(crimes)
set.seed(123)
shuffle <- sample.int(n)
shuffle <- cut(shuffle, breaks = c(0, quantile(1:n, 0.75), n), labels = c("train", "test"))
crimes.train <- split(crimes, shuffle)$train
crimes.test <- split(crimes, shuffle)$test
```


####Logistic Regression
```{r echo = FALSE}
crimes.logistic <- glm(night ~ downtown + area + DIST + BIG_ZONE + chrgdesc, data = crimes.train, family = "binomial")

# Compute the confusion matrix
crimes.logistic.prob <- predict(crimes.logistic, crimes.test, type = "response")
crimes.logistic.pred <- (crimes.logistic.prob > 0.5)
crimes.logistic.confusion <- table(Truth   = crimes.test$downtown,
                                 Predict = crimes.logistic.pred)
print("Confusion Matrix of Logistic Regression", quote = FALSE)
addmargins(crimes.logistic.confusion)

# Compute the proportional table
crimes.logistic.confusion.prop <- prop.table(crimes.logistic.confusion)
print("Proportional Table of Confusion Matrix", quote = FALSE)
print(addmargins(crimes.logistic.confusion.prop), digits = 3)

# Compute the row-proportional table
crimes.logistic.confusion.pred <- prop.table(crimes.logistic.confusion, 1)
```

####LDA
```{r echo = FALSE, warning=FALSE}
crimes.lda <- lda(night ~ downtown + area + DIST + BIG_ZONE + chrgdesc, data = crimes.train)

# Compute the confusion matrix
crimes.lda.pred <- predict(crimes.lda, crimes.test)$class
crimes.lda.confusion <- table(Truth   = crimes.test$night,
                              Predict = crimes.lda.pred)
print("Confusion Matrix of LDA", quote = FALSE)
addmargins(crimes.lda.confusion)

# Compute the proportional table
crimes.lda.confusion.prop <- prop.table(crimes.lda.confusion)
print("Proportional Table of Confusion Matrix", quote = FALSE)
print(addmargins(crimes.lda.confusion.prop), digits = 3)

# Compute the row-proportional table
crimes.lda.confusion.pred <- prop.table(crimes.lda.confusion, 1)
print("Row-Proportional Table of Confusion Matrix", quote = FALSE)
print(addmargins(crimes.lda.confusion.pred)[-3,], digits = 3)
```


###QDA
```{r echo = FALSE, warning=FALSE}
crimes.qda <- qda(night ~ downtown + area + DIST + BIG_ZONE + chrgdesc, data = crimes.train)

# Compute the confusion matrix
crimes.qda.pred <- predict(crimes.qda, crimes.test)$class
crimes.qda.confusion <- table(Truth   = crimes.test$night,
                              Predict = crimes.qda.pred)
print("Confusion Matrix of QDA", quote = FALSE)
addmargins(crimes.qda.confusion)

# Compute the proportional table
crimes.qda.confusion.prop <- prop.table(crimes.qda.confusion)
print("Proportional Table of Confusion Matrix", quote = FALSE)
print(addmargins(crimes.qda.confusion.prop), digits = 3)

# Compute the row-proportional table
crimes.qda.confusion.pred <- prop.table(crimes.qda.confusion, 1)
print("Row-Proportional Table of Confusion Matrix", quote = FALSE)
print(addmargins(crimes.qda.confusion.pred)[-3,], digits = 3)
```

##### Comparison

Test errors, FPRs and FNRs in all methods above are reported as follows.

|              |**Logistic Regression**|**LDA**|**QDA**|
|:------------:|:---------------------:|:-----:|:-----:|
|**Test Error**|`r format(1 - sum(diag(crimes.logistic.confusion.prop)), digits = 3)`|`r format(1 - sum(diag(crimes.lda.confusion.prop)), digits = 3)`|`r format(1 - sum(diag(crimes.qda.confusion.prop)), digits = 3)`|
|**FPR**       |`r format(crimes.logistic.confusion.pred[1,2], digits = 3)`|`r format(crimes.lda.confusion.pred[1,2], digits = 3)`|`r format(crimes.qda.confusion.pred[1,2], digits = 3)`|
|**FNR**       |`r format(crimes.logistic.confusion.pred[2,1], digits = 3)`|`r format(crimes.lda.confusion.pred[2,1], digits = 3)`|`r format(crimes.qda.confusion.pred[2,1], digits = 3)`|








 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
  
